Continuous developmental change can explain discontinuities in word learning

### 2019-05-14 journal/ms.tex
cogsci camera ready

% Template for Cogsci submission with R Markdown

% Stuff changed from original Markdown PLOS Template
\documentclass[10pt, letterpaper]{article}

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{float}
\usepackage{caption}

% amsmath package, useful for mathematical formulas
\usepackage{amsmath}

% amssymb package, useful for mathematical symbols
\usepackage{amssymb}

% hyperref package, useful for hyperlinks
\usepackage{hyperref}

% graphicx package, useful for including eps and pdf graphics
% include graphics with the command \includegraphics
\usepackage{graphicx}

% Sweave(-like)
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{Sinput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{Soutput}{Verbatim}{}
\DefineVerbatimEnvironment{Scode}{Verbatim}{fontshape=sl}
\newenvironment{Schunk}{}{}
\DefineVerbatimEnvironment{Code}{Verbatim}{}
\DefineVerbatimEnvironment{CodeInput}{Verbatim}{fontshape=sl}
\DefineVerbatimEnvironment{CodeOutput}{Verbatim}{}
\newenvironment{CodeChunk}{}{}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

\usepackage{color}

% Use doublespacing - comment out for single spacing
%\usepackage{setspace}
%\doublespacing

% % Text layout
% \topmargin 0.0cm
% \oddsidemargin 0.5cm
% \evensidemargin 0.5cm
% \textwidth 16cm
% \textheight 21cm

\title{Continuous developmental change can explain discontinuities in word
learning}

\usepackage{tipa}
\usepackage[rightcaption]{sidecap}

\author{{\large \bf Anonymous CogSci submission} \\  \\ \\ }

\begin{document}

\maketitle

\begin{abstract}
Cognitive development is often characterized in term of discontinuities,
but these discontinuities can sometimes be apparent rather than actual
and can arise from continuous developmental change. To explore this
idea, we use as a case study the finding by Stager and Werker (1997)
that children's early ability to distinguish similar sounds does not
automatically translate into word learning skills. Early explanations
proposed that children may not be able to encode subtle phonetic
contrasts when learning novel word meanings, thus suggesting a
discontinuous/stage-like pattern of development. However, later work has
revealed (e.g., through using simpler testing methods) that children do
encode such contrasts, thus favoring a continuous pattern of
development. Here we propose a probabilistic model describing how
development may proceed in a continuous fashion across the lifespan. The
model accounts for previously documented facts and provides new
predictions. We collected data from preschool children and adults, and
we showed that the model can explain various patterns of learning both
within the same age and across development. The findings suggest that
major aspects of cognitive development that are typically thought of as
discontinuities, may emerge from simpler, continuous mechanisms.

\textbf{Keywords:}
word learning, cognitive development, computational modeling
\end{abstract}

@@

We use a case study from word learning literature. Stager \& Werker
(1997) first showed that children's early ability to distinguish similar
sounds does not automatically translate into word learning skills.
Indeed, though infants around 14-month old can distinguish similar sound
pairs such as ``dih'' and ``bih'', they appear to fail in mapping this
pair to two different objects. Follow-up studies has focused on
proposing possible explanations for this observed gap between speech
perception and word learning (e.g., Fennell \& Waxman, 2010; Hofer \&
Levy, 2017; Rost \& McMurray, 2009; Stager \& Werker, 1997).

By around 17 m.o, children succeed in the same task (Werker, Fennell,
Corcoran, \& Stager, 2002). How does development proceed? Early accounts
assumed that children encode words in a binary way: they either fail or
succeed in encoding the relevant phonetic details (simultaneously with
the meanings). This account suggested a discontinuous/stage-like pattern
of development whereby younger children fail to encode the contrastive
phonetic detail, whereas older children succeed.

Subsequent findings have suggested otherwise. On the one hand,
14-month-olds---who typically fail in the original task---succeed when
an easier testing method is used, even under the same learning
conditions (Yoshida, Fennell, Swingley, \& Werker, 2009). They also
succeed when uncertainty is mitigated via disambiguating cues (e.g.,
Thiessen, 2007). On the other hand, adults show patterns of learning
similar to those shown by 14-month-olds when the task is more
challenging and when similarity between words increases (Pajak, Creel,
\& Levy, 2016; White, Yee, Blumstein, \& Morgan, 2013).

This pattern of evidence points towards another scenario, where the
representations are encoded in a probabilistic (rather than binary) way,
and where development is continuous, rather than stage-like (see also
Swingley, 2007). On this account, correct representations are learned
early in development, but these representations are encoded with higher
uncertainty in younger children, leading to apparent failure in
relatively demanding tasks. Development is a continuous process whereby
the initial noisy representations become more precise. In addition, more
precise representation are still imperfect: Even adults show low
accuracy learning when the sounds are subtle, e.g., non-native sounds
(Pajak et al., 2016).

We provide an intuitive illustration of how such an account explains
patterns of learning and development in Figure \ref{fig:illus}. We
observe low accuracy in word learning when the perceptual distance
between the labels is small relative to the uncertainty with which these
labels are encoded. For example, in Stager and Werker's original
experiment, children are supposed to associate label 1 (``bih'') and
label 2 (``dih'') with object 1 and object 2, respectively. Though
infants could learn that the label ``bih'' is a better match to object 1
than ``dih'', they could still judge the sound ``dih'' as a plausible
instance of the label ``bih'', thanks to the relatively large
uncertainty of the encoding, and this confusion leads to ``failure'' in
the recognition task. According to this account, accuracy in word
learning improves if we increase either the perceptual distinctiveness
of the stimuli (e.g., through using different-sounding labels), or the
precision of the encoding itself (e.g., across development).

@@

\begin{CodeChunk}
\begin{figure}[H]

{\centering \includegraphics{figs/illus-1}

@@

\caption{\label{fig:illus} An illustration of the probabilistic/continuous account using simulated data. A word is represented with a distribution over the perceptual space (indicated in red or blue). When the uncertainty of the representation is large relative to the distance between the stimuli (top panel), an instance of the red category (indicated with a star) could also be a plausible instance of the green category, hence the low recognition accuracy score. The accuracy increases when the stimuli are less similar (left panel), or when the representation are more precise (right panel).}\label{fig:illus}
\end{figure}
\end{CodeChunk}

@@

\begin{SCfigure}
\centering
\includegraphics[width=1.5in]{figs/model.png}
\caption{Graphical representation of our model. Circles indicate random variables (shading indicates observed variables). The squares indicate fixed model parameters.}
\label{fig:model}
\end{SCfigure}

A similar probabilistic structure was used by Lewis \& Frank (2013) to
model concept learning, and by Hofer \& Levy (2017) to model spoken word
learning. However, the first study assumed that the sounds are heard
unambiguously, and the second assumed the concepts are observed
unambiguously. In our model, we assume that both labels and concepts are
observed with a certain amount of perceptual noise, which we assume, for
simplicity, is captured by a normal distribution:

\[ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) \]
\[ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) \] Finally, we assume
there to be one-to-one mappings between concepts and labels and that
observers have successfully learned these mappings during the exposure
phase: \[
P(L_i|C_j) = 
\begin{cases}
  1 & \text{if  }  i=j \\  
  0  & \text{otherwise  }
\end{cases}
\]

@@

The learner hears a sound \(s\) and has to decide which object \(o\)
provides an optimal match to this sound. To this end, they must compute
the probability \(P(o|s)\) for all possible objects. This probability
can be computed by summing over all possible concepts and labels:
\[P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) \]
The joint probability \(P(o, C, L, s)\) is obtained by factoring the
Bayesian network in Figure \ref{fig:model}:
\[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \] which can be transformed using
Bayes rule into:

\[P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) \] Finally, assuming that the
concepts' prior probability is uniformly
distributed\footnote{This is a reasonable assumption in our particular case given the similarity of the concepts used in each naming situation in our experiment.},
we obtain the following expression, where all conditional dependencies
are now well defined:

@@

\begin{CodeChunk}
\begin{figure}[t]

{\centering \includegraphics{figs/task-1}

@@

\caption{\label{fig:task}An overview of the task used in this study.}\label{fig:task}
\end{figure}
\end{CodeChunk}

We use the model to predict performance in the word learning task
introduced by Stager \& Werker (1997), with a two-alternative forced
choice as in Yoshida et al. (2009). In this task, participants are first
exposed to the association between pairs of nonsense words (e.g.,
``lif''/``neem'') and pairs of objects. The word-object associations are
introduced sequentially. After this exposure phase, participants perform
a series of test trials. In each of these trials, one of the two sounds
is uttered (e.g., ``lif'') and participants choose the corresponding
object from the two alternatives. An overview of the task is shown in
Figure \ref{fig:task}.

@@

\begin{CodeChunk}
\begin{figure*}[h]

{\centering \includegraphics{figs/simulation-1}

\caption{\label{fig:simulation}The predicted probability of accurate responses in the testing phase as a function of stimuli distinctiveness $\Delta s$ and $\Delta o$ and representation precision $\sigma$ (For clarity, we assume here that $\sigma$=$\sigma_C$=$\sigma_L$). Dashed line represents chance.}\label{fig:simulation}
\end{figure*}
\end{CodeChunk}

@@

We planned to recruit a sample of N=60 children ages 4-5 years from the
Bing Nursery School on Stanford University's campus. Here we report data
from n=47 children. An additional n=28 children participated but were
removed from analyses because they were not above chance on the catch
trials due to the challenging nature of our procedure (see below). We
also planned to recruit a sample of N=60 adults on Amazon Mechanical
Turk. Data from n=10 participants were excluded due to low scores on the
catch trials (n=9 ) or because they were familiar with the non-English
sound stimuli we used in the adult experiment (n=1), yielding a final
sample of n=50.

@@

The sound stimuli were generated using the MBROLA Speech Synthesizer
(Dutoit, Pagel, Pierret, Bataille, \& Van der Vrecken, 1996). We
generated three kinds of nonsense word pairs which varied in their
degree of similarity to English speakers: 1) ``different'':
``lif''/``neem'' and ``zem''/``doof'', 2) ``intermediate'':
``aka''/``ama'' and ``ada''/``aba'', and 3) ``similar'' non-English
minimal pairs: ``ada''/``a\textipa{d\super h}a'' (in hindi) and
``a\textipa{Q}a''/``a\textipa{\textcrh}a'' (in arabic).

As for the objects, we used the Dynamic Stimuli javascript
library\footnote{https://github.com/erindb/stimuli} which allowed us to
generate objects in four different categories: ``tree'', ``bird'',
``bug'', and ``fish''. These categories are supposed to be naturally
occurring kinds that might be seen on an alien planet. In each category,
we generated ``different'', ``intermediate'' and ``similar'' pairs by
manipulating a continuous property controlling features of the
category's shape (e.g, body stretch or head fatness).

@@

\subsubsection{Design}\label{design}

Each age group saw only two of the three levels of similarity described
in the previous sub-section: ``different'' vs. ``intermediate'' for
preschoolers, and ``intermediate'' vs. ``similar'' for adults. We made
this choice in light of pilot studies showing that adults were at
ceiling with ``different'' sounds/objects, and children were at chance
with the ``similar'' sounds/objects. That said, this difference in the
level of similarity is accounted for in the model through using the
appropriate perceptual distance used in each age group (Figure
\ref{fig:stim}).

\begin{CodeChunk}
\begin{figure}[h]

{\centering \includegraphics{figs/stim-1}

@@

\caption{\label{fig:stim}Distances for both sound and object pairs from an adult norming study. Data represent Likert values normalized to [0,1] interval. Error bars represent 95\% confidence intervals.}\label{fig:stim}
\end{figure}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{figure*}[h]

{\centering \includegraphics{figs/all_data-1}

@@

\caption{\label{fig:data_all}Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs. adults). We show both experimental results (solid lines) and model predictions (dashed lines). Error bars represent 95\% confidence intervals.}\label{fig:all_data}
\end{figure*}
\end{CodeChunk}

In the exposure trials, participants saw two objects associated with
their corresponding sounds. We presented the first object on the left
side of the tablet's screen simultaneously with the corresponding sound.
The second sound-object association followed on the other side of the
screen after 500ms. For both objects, visual stimuli were present for
the duration of the sound clip (∼800ms). In the testing trials,
participants saw both objects simultaneously and heard only one sound.
They completed the trial by selecting which of the two objects
corresponded to the sound. The object-sound pairings were randomized
across participants, as was the order of the conditions (except for the
catch condition which was always placed in the middle of the testing
sequence). We also randomized the on-screen position (left vs.~right) of
the two pictures on each testing trial.

Experimental results are shown in Figure 6 (solid lines). We first
analyzed the results using a mixed-effects logistic regression with
sound distance, object distance and age group as fixed effects, and with
a maximal random effects structure (allowing us to take into account the
full nested structure of our data) (Barr, Levy, Scheepers, \& Tily,
2013). We found main effects for all the fixed effects in the
regression. For the sound distance, we obtained \(\beta =\) 0.44 (\(p\)
\textless{} 0.001), replicating previous findings. For object distance,
we found \(\beta =\) 0.5 (\(p\) \textless{} 0.001), and this finding
confirms the new prediction of our model. Finally, for the age group, we
obtained \(\beta =\) 0.43 (\(p\) \textless{} 0.001), showing that
performance improves with age. In addition, we found two-way
interactions between sound distance and age (\(\beta =\) 0.17, \(p\)
\textless{}0.05) and between object distance and age (\(\beta =\) 0.18,
\(p\) \textless{}0.05).

We next fit our model (using Equation 2) to the participants' responses
in each age group. The values of \(\Delta s\) and \(\Delta o\) were set
based on data from the similarity judgment task (Figure \ref{fig:stim}).
Thus, the model has two degrees of freedom for each group, i.e.,
\(\sigma_C\) and \(\sigma_L\). Figure \ref{fig:data_all} (dashed lines)
shows the predictions. The model captures the qualitative patterns in
both age groups: starting from a low accuracy recognition when both the
sound and object distances are small, the model correctly predicts an
increase in accuracy when either the sound distance or the object
distance increases. Further, accuracy is correctly predicted to be
maximal when both the sound and object distances are high.

The values of the parameters were as follows. Children had a
label-specific uncertainty of \(\sigma_S =\) 0.9 {[}0.68,
1.11{]}\footnote{All uncertainty intervals in this paper represent 95\% Confidence Intervals.},
and a concept-specific uncertainty of \(\sigma_C =\) 0.29 {[}0.1,
0.49{]}. Adults had a label-specific uncertainty of \(\sigma_S =\) 0.14
{[}-0.02, 0.3{]}, and a concept-specific uncertainty of \(\sigma_C =\)
0.19 {[}0.04, 0.34{]}. As predicted, the uncertainty parameters were
larger for children than they were for adults, showing that the
probabilistic representations becomes more refined (that is, \(\sigma\)
becomes smaller) across development. The developmental effect was more
important for the label-specific uncertainty.

The models explained the majority of the variance in the participants'
mean responses (\(R^2=\) 0.86, for the combined adult and children's
data). To investigate whether the model's predictive power was due to
overfitting, we fit a simplified version with only one degree of freedom
(i.e., a single variance common to both sounds and objects). This
single-variance model explained as much variance in the mean responses
(\(R^2=\) 0.87). It also captured the main qualitative patterns (graph
not shown), suggesting that the explanatory power of the model is
largely due to its structure, rather than its degrees of freedom.

@@

\setlength{\parindent}{-0.1in} \setlength{\leftskip}{0.125in} \noindent

>>>>

\documentclass[english,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Continuous developmental change can explain discontinuities in word learning},
            pdfauthor={Abdellah Fourtassi, Sophie Regan, \& Michael C. Frank},
            pdfkeywords={word learning, cognitive development, computational modeling},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{Continuous developmental change can explain discontinuities in word
learning}
    \author{Abdellah Fourtassi\textsuperscript{1}, Sophie Regan\textsuperscript{1},
\& Michael C. Frank\textsuperscript{1}}
    \date{}

\shorttitle{Continuous Development of Word Learning}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Psychology, Stanford University}
\keywords{word learning, cognitive development, computational modeling}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\usepackage{lineno}

\linenumbers
\usepackage{tipa}
\usepackage[sortcites=false,sorting=none]{biblatex}

\authornote{ Abdellah Fourtassi

Department of Psychology

Stanford University

50 Serra Mall

Jordan Hall, Building 420

Stanford, CA 94301

Correspondence concerning this article should be addressed to Abdellah
Fourtassi, Postal address. E-mail:
\href{mailto:afourtas@stanford.edu}{\nolinkurl{afourtas@stanford.edu}}}

\abstract{
``Cognitive development is often characterized in term of
discontinuities, but these discontinuities can sometimes be apparent
rather than actual and can arise from continuous developmental change.
To explore this idea, we use as a case study the finding by Stager and
Werker (1997) that children's early ability to distinguish similar
sounds does not automatically translate into word learning skills. Early
explanations proposed that children may not be able to encode subtle
phonetic contrasts when learning novel word meanings, thus suggesting a
discontinuous/stage-like pattern of development. However, later work has
revealed (e.g., through using simpler testing methods) that children do
encode such contrasts, thus favoring a continuous pattern of
development. Here we propose a probabilistic model describing how
development may proceed in a continuous fashion across the lifespan. The
model accounts for previously documented facts and provides new
predictions. We collected data from preschool children and adults, and
we showed that the model can explain various patterns of learning both
within the same age and across development. The findings suggest that
major aspects of cognitive development that are typically thought of as
discontinuities, may emerge from simpler, continuous mechanisms.''

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle

@@

We use a case study from word learning literature. Stager and Werker
(1997) first showed that children's early ability to distinguish similar
sounds does not automatically translate into word learning skills.
Indeed, though infants around 14-month old can distinguish similar sound
pairs such as \enquote{dih} and \enquote{bih}, they appear to fail in
mapping this pair to two different objects.

By around 17 m.o, children succeed in the same task (Werker, Fennell,
Corcoran, \& Stager, 2002). How does development proceed? The answer to
this question depends on the nature of the chidlren's word encoding in
the task. Early accounts assumed that children encode words in a rather
binary way: they either fail or succeed in attending to the relevant
phonetic details (simultaneously with the meanings). In the orginal
paper, Stager and Werker (1997) noted that \enquote{Infants of 14 months
fail to detect the same phonetic detail that they can easily detect in a
simple syllable discrimination task}. They argued that the high cogntive
demands of the task make children experience a limitation in the amount
of phonetic details they can access. In a similar vein, Pater et al.
(2004) argued that \enquote{when a contrast is first acquired, it is not
stable and can be lost under processing demands}. This binary account
suggested a discontinuous/stage-like pattern of development whereby
younger children fail to encode the contrastive phonetic detail, whereas
older children succeed.

Subsequent findings have investigated the implications of this
hypothesis in both infants and adults. First, if the demands of the task
totally empede the encoding of subtle phonetic contrasts, then infants
should fail in learning the mappings between the sounds and the objects,
regardless of how this learning is probed. However, 14-month-olds
succeed in this task under the same \emph{learning} conditions as in
Stager and Werker (1997), but when an easier \emph{testing} method is
used (Yoshida, Fennell, Swingley, \& Werker, 2009). Second, if the
minsmatch between sound distrimination and word learning is only related
to limited cognitive resources in infancy, then adults --- who have
greater attentianal and working memory capacity --- should always
succeed in mapping pairs of sounds they can discriminate to different
objects. Nonetheless, even adults show patterns learning that mirror
those shown by 14-month-olds (Pajak, Creel, \& Levy, 2016; White, Yee,
Blumstein, \& Morgan, 2013).

This new set of evidence points towards another scenario, where the
representations are encoded in a probabilistic (rather than binary) way,
and where development is continuous, rather than stage-like (see also
Swingley, 2007). On this account, correct representations are learned
early in development, but these representations are encoded with higher
uncertainty in younger children, leading to \emph{apparent} failure in
relatively demanding tasks. Development is a continuous process whereby
the initial noisy representations become more precise. Crucially, in a
probabilsitic account, more precise representation do not mean they
perfect, thus accounting for the fact that even adults show low accuracy
learning when the sounds are subtle, e.g., non-native (Pajak et al.,
2016).

We provide an intuitive illustration of how such an account explains
patterns of learning and development in Figure \ref{fig:illus}. We
observe low accuracy in word learning when the perceptual distance
between the labels is small relative to the uncertainty with which these
labels are encoded. For example, in Stager and Werker's original
experiment, children are supposed to associate label 1 (\enquote{bih})
and label 2 (\enquote{dih}) with object 1 and object 2, respectively.
Though infants could learn that the label \enquote{bih} is a better
match to object 1 than \enquote{dih}, they could still judge the sound
\enquote{dih} as a plausible instance of the label \enquote{bih}, thanks
to the relatively large uncertainty of the encoding, and this confusion
leads to \enquote{failure} in the recognition task. According to this
account, accuracy in word learning improves if we increase either the
perceptual distinctiveness of the stimuli (e.g., through using
different-sounding labels), or the precision of the encoding itself
(e.g., across development).

@@

\begin{figure}

{\centering \includegraphics[width=300px]{figs/illustration}

@@

\caption{An illustration of the probabilistic/continuous account using simulated data. A word is represented with a distribution over the perceptual space (indicated in red or blue). When the uncertainty of the representation is large relative to the distance between the stimuli (top panel), an instance of the red category (indicated with a star) could also be a plausible instance of the green category, hence the low recognition accuracy score. The accuracy increases when the stimuli are less similar (left panel), or when the representation are more precise (right panel).}\label{fig:illus}
\end{figure}

@@

\begin{figure}

{\centering \includegraphics[width=300px]{figs/model}

\caption{Graphical representation of our model. Circles indicate random variables (shading indicates observed variables). The squares indicate fixed model parameters.}\label{fig:model}
\end{figure}

A similar probabilistic structure was used by Lewis and Frank (2013) to
model concept learning, and by Hofer and Levy (2017) to model spoken
word learning. However, the first study assumed that the sounds are
heard unambiguously, and the second assumed the concepts are observed
unambiguously. In our model, we assume that both labels and concepts are
observed with a certain amount of perceptual noise, which we assume, for
simplicity, is captured by a normal distribution:

\[ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) \]

\[ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) \]

Finally, we assume there to be one-to-one mappings between concepts and
labels and that observers have successfully learned these mappings
during the exposure phase: \[
P(L_i|C_j) = 
\begin{cases}
  1 & \text{if  }  i=j \\  
  0  & \text{otherwise  }
\end{cases}
\]

@@

The learner hears a sound \(s\) and has to decide which object \(o\)
provides an optimal match to this sound. To this end, they must compute
the probability \(P(o|s)\) for all possible objects. This probability
can be computed by summing over all possible concepts and labels:
\[P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) \]

The joint probability \(P(o, C, L, s)\) is obtained by factoring the
Bayesian network in Figure \ref{fig:model}:
\[P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) \]

which can be transformed using Bayes rule into:

\[P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) \]

Finally, assuming that the concepts' prior probability is uniformly
distributed\footnote{This is a reasonable assumption in our particular case given the similarity of the concepts used in each naming situation in our experiment.},
we obtain the following expression, where all conditional dependencies
are now well defined:

@@

\begin{figure}[t]

{\centering \includegraphics[width=3.75in]{figs/task}

@@

\caption{An overview of the task used in this study.}\label{fig:task}
\end{figure}

We use the model to predict performance in the word learning task
introduced by Stager and Werker (1997), with a two-alternative forced
choice as in Yoshida et al. (2009). In this task, participants are first
exposed to the association between pairs of nonsense words (e.g.,
\enquote{lif}/\enquote{neem}) and pairs of objects. The word-object
associations are introduced sequentially. After this exposure phase,
participants perform a series of test trials. In each of these trials,
one of the two sounds is uttered (e.g., \enquote{lif}) and participants
choose the corresponding object from the two alternatives. An overview
of the task is shown in Figure \ref{fig:task}.

@@

\begin{figure}[htbp]
\centering
\includegraphics{ms_files/figure-latex/simulation-1.pdf}
\caption{\label{fig:simulation}The predicted probability of accurate
responses in the testing phase as a function of stimuli distinctiveness
\(\Delta s\) and \(\Delta o\) and representation precision \(\sigma\)
(For clarity, we assume here that \(\sigma\)=\(\sigma_C\)=\(\sigma_L\)).
Dashed line represents chance.}
\end{figure}

@@

We planned to recruit a sample of N=60 children ages 4-5 years from the
Bing Nursery School on Stanford University's campus. Here we report data
from n=55 children. An additional n=35 children participated but were
removed from analyses because they were not above chance on the catch
trials due to the challenging nature of our procedure (see below). We
also planned to recruit a sample of N=60 adults on Amazon Mechanical
Turk. Data from n=26 participants were excluded due to low scores on the
catch trials (n=26 ) or because they were familiar with the non-English
sound stimuli we used in the adult experiment (n=0), yielding a final
sample of n=74.

@@

The sound stimuli were generated using the MBROLA Speech Synthesizer
(Dutoit, Pagel, Pierret, Bataille, \& Van der Vrecken, 1996). We
generated three kinds of nonsense word pairs which varied in their
degree of similarity to English speakers: 1) \enquote{different}:
\enquote{lif}/\enquote{neem} and \enquote{zem}/\enquote{doof}, 2)
\enquote{intermediate}: \enquote{aka}/\enquote{ama} and
\enquote{ada}/\enquote{aba}, and 3) \enquote{similar} non-English
minimal pairs: \enquote{ada}/\enquote{a\textipa{d\super h}a} (in hindi)
and \enquote{a\textipa{Q}a}/\enquote{a\textipa{\textcrh}a} (in arabic).

As for the objects, we used the Dynamic Stimuli javascript
library\footnote{https://github.com/erindb/stimuli} which allowed us to
generate objects in four different categories: \enquote{tree},
\enquote{bird}, \enquote{bug}, and \enquote{fish}. These categories are
supposed to be naturally occurring kinds that might be seen on an alien
planet. In each category, we generated \enquote{different},
\enquote{intermediate} and \enquote{similar} pairs by manipulating a
continuous property controlling features of the category's shape (e.g,
body stretch or head fatness).

@@

\includegraphics{ms_files/figure-latex/unnamed-chunk-6-1.pdf}
\#\#\#Design

Each age group saw only two of the three levels of similarity described
in the previous sub-section: \enquote{different} vs.
\enquote{intermediate} for preschoolers, and \enquote{intermediate} vs.
\enquote{similar} for adults. We made this choice in light of pilot
studies showing that adults were at ceiling with \enquote{different}
sounds/objects, and children were at chance with the \enquote{similar}
sounds/objects. That said, this difference in the level of similarity is
accounted for in the model through using the appropriate perceptual
distance used in each age group (Figure \ref{fig:stim}).

\begin{figure}[h]

{\centering \includegraphics{ms_files/figure-latex/stim-1}

@@

\caption{Distances for both sound and object pairs from an adult norming study. Data represent Likert values normalized to [0,1] interval. Error bars represent 95\% confidence intervals.}\label{fig:stim}
\end{figure}

@@

In the exposure trials, participants saw two objects associated with
their corresponding sounds. We presented the first object on the left
side of the tablet's screen simultaneously with the corresponding sound.
The second sound-object association followed on the other side of the
screen after 500ms. For both objects, visual stimuli were present for
the duration of the sound clip (about 800ms). In the testing trials,
participants saw both objects simultaneously and heard only one sound.
They completed the trial by selecting which of the two objects
corresponded to the sound. The object-sound pairings were randomized
across participants, as was the order of the conditions (except for the
catch condition which was always placed in the middle of the testing
sequence). We also randomized the on-screen position (left vs.~right) of
the two pictures on each testing trial.

\begin{figure}[h]

{\centering \includegraphics{ms_files/figure-latex/allData-1}

@@

\caption{Accuracy of novel word recognition as as a function of the sound distance, the object distance, and the age group (preschool children vs. adults). We show both experimental results (solid lines) and model predictions (dashed lines). Error bars represent 95\% confidence intervals.}\label{fig:allData}
\end{figure}

Experimental results are shown in Figure \ref{fig:allData} (solid
lines). We first analyzed the results using a mixed-effects logistic
regression with sound distance, object distance and age group as fixed
effects, and with a maximal random effects structure (allowing us to
take into account the full nested structure of our data) (Barr, Levy,
Scheepers, \& Tily, 2013). We found main effects for all the fixed
effects in the regression. For the sound distance, we obtained
\(\beta =\) 0.52 (\(p\) \textless{} 0.001), replicating previous
findings. For object distance, we found \(\beta =\) 0.83 (\(p\)
\textless{} 0.001), and this finding confirms the new prediction of our
model. Finally, for the age group, we obtained \(\beta =\) 0.76 (\(p\)
\textless{} 0.001), showing that performance improves with age. In
addition, we found two-way interactions between sound distance and age
(\(\beta =\) 0.15, \(p\) = 0.17) and between object distance and age
(\(\beta =\) 0.45, \(p\) \textless{} 0.001).

We next fit our model (using Equation 2) to the participants' responses
in each age group. The values of \(\Delta s\) and \(\Delta o\) were set
based on data from the similarity judgment task (Figure \ref{fig:stim}).
Thus, the model has two degrees of freedom for each group, i.e.,
\(\sigma_C\) and \(\sigma_L\). Figure \ref{fig:allData} (dashed lines)
shows the predictions. The model captures the qualitative patterns in
both age groups: starting from a low accuracy recognition when both the
sound and object distances are small, the model correctly predicts an
increase in accuracy when either the sound distance or the object
distance increases. Further, accuracy is correctly predicted to be
maximal when both the sound and object distances are high.

The values of the parameters were as follows. Children had a
label-specific uncertainty of \(\sigma_S =\) 0.83 {[}0.64,
1.02{]}\footnote{All uncertainty intervals in this paper represent 95\% Confidence Intervals.},
and a concept-specific uncertainty of \(\sigma_C =\) 0.31 {[}0.11,
0.51{]}. Adults had a label-specific uncertainty of \(\sigma_S =\) 0.12
{[}0.12, 0.13{]}, and a concept-specific uncertainty of \(\sigma_C =\)
0.17 {[}0.16, 0.18{]}. As predicted, the uncertainty parameters were
larger for children than they were for adults, showing that the
probabilistic representations becomes more refined (that is, \(\sigma\)
becomes smaller) across development. The developmental effect was more
important for the label-specific uncertainty.

The models explained the majority of the variance in the participants'
mean responses (\(R^2=\) 1, for the combined adult and children's data).
To investigate whether the model's predictive power was due to
overfitting, we fit a simplified version with only one degree of freedom
(i.e., a single variance common to both sounds and objects). This
single-variance model explained as much variance in the mean responses
(\(R^2=\) 0.95). It also captured the main qualitative patterns (graph
not shown), suggesting that the explanatory power of the model is
largely due to its structure, rather than its degrees of freedom.

@@

\setlength{\parindent}{-0.5in} \setlength{\leftskip}{0.5in}
